EuPPollNet: A European database of plant-pollinator networks

### 2024-08-14 Manuscript/EuPPollNet_Ms.qmd
percent fo orders per study

@@

The database contains `r study_number` independent published and unpublished studies conducted during the time period `r min_year` - `r max_year` in `r country_number` different countries (**Figure 1a** and **Figure 1b**). The studies differ in sampling effort and methodology, and thus documenting sampling methods and sampling effort is an important feature of EuPPollNet. Most studies took place within a single flowering season (`r format(round(one_year, 2), nsmall = 2)`%), sampled a given location for an average of `r format(round(average_sampling_days, 2), nsmall=2)` days, and documented interactions mostly by using `r  most_common_method[[1]]` as the sampling method (`r format(round(most_common_method[[3]], 2), nsmall = 2)`%). The database includes a total of `r prettyNum(interaction_number, big.mark=",")` distinct interactions. Most of the pollinator species belong to the orders Hymenoptera, Diptera, Lepidoptera and Coleoptera (`r format(round(spp_percent_main_order, 2), nsmall = 2)`%), which account for nearly all interactions in this database (`r format(round(main_orders_percent, 2), nsmall = 2)`%). Species that belong to other orders `r format(round(100-spp_percent_main_order, 2), nsmall = 2)`% are not explored in this study as they conduct a minor fraction of the total interactions (`r format(round(100-main_orders_percent, 2), nsmall = 2)`%). Hymenoptera and Diptera contain the highest number of species comprising each approximately 1,000 species in the database. However, the majority of plant-pollinator interactions are from Hymenoptera species (`r format(round(Hymenoptera_interactions, 2), nsmall = 2)`%; **Figure 1c**). Notably, the western honey bee, _Apis mellifera_, represents `r format(round(apis_percent, 2), nsmall = 2)`% of the total interaction records from the database and an average of `r format(round(apis_average_network, 2), nsmall = 2)`% of the total interactions per network.

>>>>

#Calculate percentage of studies that recorded the main 4 orders
metadata = readRDS("../Data/3_Final_data/Metadata.rds")
#Some studies are divided by year
#Get an average of the pollinator percentages across years first
#Fix NA's
metadata_study = metadata %>%
group_by(Study_id) %>% 
mutate(Hymenoptera_percent = as.numeric(na_if(Hymenoptera_percent, "NA"))) %>%  
mutate(Diptera_percent = as.numeric(na_if(Diptera_percent, "NA"))) %>%  
mutate(Lepidoptera_percent = as.numeric(na_if(Lepidoptera_percent, "NA"))) %>%  
mutate(Coleoptera_percent = as.numeric(na_if(Coleoptera_percent, "NA"))) 
#Calculate average
mean_study = metadata_study  %>% 
summarise(Hymenoptera_percent = mean(Hymenoptera_percent, na.rm = T),
          Diptera_percent = mean(Diptera_percent, na.rm = T),
          Lepidoptera_percent = mean(Lepidoptera_percent, na.rm = T),
          Coleoptera_percent = mean(Coleoptera_percent, na.rm = T)) %>% 
 mutate(across(c(Hymenoptera_percent, Diptera_percent, Lepidoptera_percent, Coleoptera_percent),
                ~ ifelse(is.nan(.), NA, .))) 
#Now calculate percentage of studies that record any of these 4 orders
mean_percent_order = mean_study %>%
  summarise(
    Hymenoptera_percent_metaweb = sum(!is.na(Hymenoptera_percent)) / nrow(.) * 100,
    Diptera_percent_metaweb = sum(!is.na(Diptera_percent)) / nrow(.) * 100,
    Lepidoptera_percent_metaweb = sum(!is.na(Lepidoptera_percent)) / nrow(.) * 100,
    Coleoptera_percent_metaweb = sum(!is.na(Coleoptera_percent)) / nrow(.) * 100)

Hymenoptera_percent_metaweb = mean_percent_order$Hymenoptera_percent_metaweb
Diptera_percent_metaweb = mean_percent_order$Diptera_percent_metaweb
Lepidoptera_percent_metaweb = mean_percent_order$Lepidoptera_percent_metaweb
Coleoptera_percent_metaweb = mean_percent_order$Coleoptera_percent_metaweb

@@

The database contains `r study_number` independent published and unpublished studies conducted during the time period `r min_year` - `r max_year` in `r country_number` different countries (**Figure 1a** and **Figure 1b**). The studies differ in sampling effort and methodology, and thus documenting sampling methods and sampling effort is an important feature of EuPPollNet. Most studies took place within a single flowering season (`r format(round(one_year, 2), nsmall = 2)`%), sampled a given location for an average of `r format(round(average_sampling_days, 2), nsmall=2)` days, and documented interactions mostly by using `r  most_common_method[[1]]` as the sampling method (`r format(round(most_common_method[[3]], 2), nsmall = 2)`%).

`r format(round(Hymenoptera_percent_metaweb, 2), nsmall = 2)`% of the studies documented interactions from Hymenoptera, `r format(round(Diptera_percent_metaweb, 2), nsmall = 2)`% from Diptera, `r format(round(Lepidoptera_percent_metaweb, 2), nsmall = 2)`% from Lepidoptera, and `r format(round(Coleoptera_percent_metaweb, 2), nsmall = 2)`% from Coleoptera.

The database includes a total of `r prettyNum(interaction_number, big.mark=",")` distinct interactions. Most of the pollinator species belong to the orders Hymenoptera, Diptera, Lepidoptera and Coleoptera (`r format(round(spp_percent_main_order, 2), nsmall = 2)`%), which account for nearly all interactions in this database (`r format(round(main_orders_percent, 2), nsmall = 2)`%). Species that belong to other orders `r format(round(100-spp_percent_main_order, 2), nsmall = 2)`% are not explored in this study as they conduct a minor fraction of the total interactions (`r format(round(100-main_orders_percent, 2), nsmall = 2)`%). Hymenoptera and Diptera contain the highest number of species comprising each approximately 1,000 species in the database. However, the majority of plant-pollinator interactions are from Hymenoptera species (`r format(round(Hymenoptera_interactions, 2), nsmall = 2)`%; **Figure 1c**). Notably, the western honey bee, _Apis mellifera_, represents `r format(round(apis_percent, 2), nsmall = 2)`% of the total interaction records from the database and an average of `r format(round(apis_average_network, 2), nsmall = 2)`% of the total interactions per network.
